No Replication Without Process Documentation:  An Assessment of Management

### 2020-04-02 R/MSE manuscript.Rmd
Edit objectives and methods for climate change citations and counts

We also conduct a focused analysis of MSE processes that address the influence of climate change on fisheries management, highlighting aspects of MSE processes that model climate change as a driver of system status.

# Methods 
## Finding and Sampling the MSE Literature 
We conducted our search for MSEs in the SCI-EXPANDED index from Web of Science, searching for “management strategy evaluation” by topic across all years on January 8th, 2019. This search returned 264 results.  We reviewed a random sample of 30 articles that document a MSE, removing articles that were reviews, meta-analyses, or simply cited other MSE articles from our sample. After removing other articles from the original set of 264 articles, 154 articles document a MSE and 13 of these included climate change as a driver of fishery status. To give as full a picture of the climate change MSE to date as possible we have also reviewed the additional climate change MSE

| MSE type | Count |
|:--:|:--:|
| Published | 154 |
| Random Sample | 30 |
| Climate Change | 13 |  
*Estimated by extrapolating from the assessed MSEs to the full set for now, the submission will contain an final count.

>>>>

An incresingly recognized challenge in fisheries management is responding to changes in the productivity of fisheries stocks as a result of climate change [@busch_climate_2016, @brander_global_2007]. We also conduct a focused analysis of MSE processes that address the influence of climate change on fisheries management, highlighting aspects of MSE processes that model climate change as a driver of system status.

# Methods 
## Finding and Sampling the MSE Literature 
We conducted our search for MSEs in the SCI-EXPANDED index from Web of Science, searching for “management strategy evaluation” by topic across all years on January 8th, 2019. This search returned 264 results.  We reviewed a random sample of 30 articles that document a MSE (supplement 2), removing articles that were reviews, meta-analyses, or simply cited other MSE articles from our sample. After removing other articles from the original set of 264 articles, 154 articles document a MSE.  We reviewed 16 climate change MSE articles (supplement 2). Twelve of these articles came from our original search.  To give as full a picture of the climate change MSE articles to date as possible we also reviewed the 4 additional climate change MSE articles published in 2019.

| MSE type | Count |
|:--:|:--:|
| Published | 154 |
| Random Sample | 30 |
| Climate Change | 12 |
